### 2025-01-17 paper/main.tex
added new materials

% --- packages --------------------------------------------------------
\usepackage{textcomp}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[english]{babel}
\usepackage{booktabs}
\usepackage{setspace}
\usepackage[centering, left=3.5cm, right=2.5cm, textheight=24cm]{geometry}

@@

\vspace*{0.5cm}
Studium <licencjackie/magisterskie>\\
\begin{flushleft}
Kierunek: Metody Ilościowe w Ekonomii i System Informacyjne\\
%Specjalność: <specjalność> % w przypadku braku należy pominać
%Forma studiów: <forma studiów (stacjonarne, itd.)>
\end{flushleft}

\vspace*{.5cm}
\rule{0cm}{1cm}\hfill
\begin{minipage}{9cm}
Imię i nazwisko autora: <name and family name>\\
Nr albumu: <12345>
\end{minipage}

\vspace*{1cm}
\begin{minipage}{12cm}
\centering
\Large
\textbf{<title>}
\end{minipage}

\vspace*{2cm}
\rule{0cm}{1cm}\hfill
\begin{minipage}{9cm}
Praca <licencjacka/magisterska> napisana\\
w Instytucie Ekonomii Matematycznej\\
pod kierunkiem naukowym\\
dr hab. Michała Ramszy
\end{minipage}

\vfill
Warszawa <year>
\end{titlepage}

>>>>

% --- packages --------------------------------------------------------
\usepackage{textcomp}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[english]{babel}
\usepackage{booktabs}
\usepackage{setspace}
\usepackage{csquotes}
\usepackage[centering, left=3.5cm, right=2.5cm, textheight=24cm]{geometry}

@@

\vspace*{0.5cm}
Master's study\\
\begin{flushleft}
Field of study: Advanced Analytics – Big Data\\
%Specjalność: <specjalność> % w przypadku braku należy pominać
%Forma studiów: <forma studiów (stacjonarne, itd.)>
\end{flushleft}

\vspace*{.5cm}
\rule{0cm}{1cm}\hfill
\begin{minipage}{9cm}
Author's first name and surname: Bogdan Bojarin\\
Student's register No.: 75184
\end{minipage}

\vspace*{1cm}
\begin{minipage}{12cm}
\centering
\Large
\textbf{Development of an intelligent system of document processing and generation based on machine learning methods}
\end{minipage}

\vspace*{2cm}
\rule{0cm}{1cm}\hfill
\begin{minipage}{9cm}
Master's thesis:\\
under the scientific supervision of:\\
dr hab. Michał Ramsza\\
written in\\
Institute of Mathematical Economics\\
\end{minipage}

\vfill
Warsaw 2025
\end{titlepage}
